Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-03-07 main.tex
new figures 2 and 6 (WIP)

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/makespan_relations_by_wf_size2}
    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/makespan_relations_by_wf_size-constrained2}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}

>>>>

\begin{figure}[tb]
    \centering
  \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size_barplot}
    \vspace{-0.8cm}
    \caption{Relative makespans of heuristics normalized by \heft makespan, by workflow
    size, on default cluster. Smaller is better.}
    \label{fig:ms-relations-by-workflow}
    \vspace{-0.15cm}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/ms_relations_by_wf_size-constrained-barplot}
    \caption{Relative makespans on the memory-constrained cluster.
%        produced by the heuristics to the makespan produced by the baseline, by workflow size.
    Smaller is better.}
    \label{fig:ms-relations-by-workflow-constrained}
    \vspace{-0.15cm}
\end{figure}
